ODGI: understanding pangenome graphs

### 2021-11-09 manuscript/main.tex
pwg name

We thank members of the HPRC ``Pangenomes Working Group'' for their insightful discussion and feedback, and members of the HPRC production teams for their development of resources used in our exposition.

>>>>

We thank members of the HPRC Pangenome Working Group for their insightful discussion and feedback, and members of the HPRC production teams for their development of resources used in our exposition.
